Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and correlation with baryon disk properties

### 2019-07-17 Document/paper.tex
edit

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disk.pdf}
\end{center}
\caption{A}
\label{fig:disk_correlations}
\end{figure*}

@@

Although the analytic expression is meant to be used on the outer
regions of logarithmic axisymmetric halos, it works well as a first
approximation for nearly axisymmetric halos as those produced by our
simulations 
We find that the difference between the measured and the
approximated isopotential axial ratios is not bigger than $quantity
percent$ {\bf }.

{\bf Aqui hace falta una grafica comparando explicitamente los
  valores para q y para s, esto para diferentes radios.
  Otro punto importante es que se tiene q, pero como se
  relaciona s?
  Ademas hay que calcularlos para los radius aproximados que se
  presentan en las tablas observacionales y en las de simulaciones.
  10-20kpc se acerca a 1/8Rvir, 20-25 1/4Rvir, 60kpc aproximadamente 1/2Rvir
}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disk.pdf}
\end{center}
\caption{Correlations between the halo triaxility at different radii
  and disk properties. 
In all cases there is a label showing the value of the Spearman's rank
correlation coefficient.}
\label{fig:disk_correlations}
\end{figure*}

@@

Although the analytic expression is meant to be used on the outer
regions of logarithmic axisymmetric halos, it works well as a first
approximation for nearly axisymmetric halos as those produced by our
simulations 
We find that the difference between the measured and the
approximated isopotential axial ratios is not bigger than $quantity
percent$.
